### 2019-04-09 Bucketing/background.tex
Include sizes in paper

\iffalse % TODO{2019-03-15}: Make this more formal?
 V \in Var
 F \in Fun
 T \in Term
 T ::= V | F | T1 T2

@@

\iffalse TODO{2019-03-15} In fact, there are similarities between the way a TE
system like \qspec{} can generalise from checking \emph{particular} properties
to \emph{inventing} new ones, and the way counterexample finders like \qcheck{}
can generalise from testing \emph{particular} expressions to \emph{inventing}
expressions to test. One of our aims is to understand the implications of this
generalisation, the lessons that each can learn from the other's approach to
term generation, and the consequences for testing and QA in general.  \fi

@@

% TODO{2019-03-15}

>>>>

\iffalse % TODO{2019-04-09}: Make this more formal?
 V \in Var
 F \in Fun
 T \in Term
 T ::= V | F | T1 T2

@@

\iffalse TODO{2019-04-09} In fact, there are similarities between the way a TE
system like \qspec{} can generalise from checking \emph{particular} properties
to \emph{inventing} new ones, and the way counterexample finders like \qcheck{}
can generalise from testing \emph{particular} expressions to \emph{inventing}
expressions to test. One of our aims is to understand the implications of this
generalisation, the lessons that each can learn from the other's approach to
term generation, and the consequences for testing and QA in general.  \fi

@@

% TODO{2019-04-09}
